Information Disclosure in Dynamic Innovation Contests

### 2025-05-16 paper/Paper.tex
update

1. How to select key players? Top $n$ in final private leaderboard

>>>>

1. How to select key players?

One simple and intuitive approach is to identify the two strongest teams in each contest.
This approach rests on an implicit assumption: that participants have a basic understanding of each other’s relative strength. 
In the context of Kaggle competitions, this is a reasonable premise: 
Team compositions are openly displayed, and individual profiles provide detailed historical records—such as past rankings, medal counts, and shared notebooks—which help participants quickly assess the technical strength of their rivals. 
Moreover, forum discussions and public notebooks foster a semi-transparent environment where ideas and methods are informally exchanged. 
Together, these features enable top teams to identify likely competitors and adjust their strategies accordingly.
